\documentclass[11pt]{report}              % Book class in 11 points
\usepackage{mcs_pack}
\usepackage{chngcntr}

\input{pf.tex}
\input{psfig.tex}
\input{commands.tex}
\usepackage{fancyvrb}
\newcommand\verbbf[1]{\textcolor[rgb]{0,0,1}{#1}}
\usepackage{tabularx}  % for 'tabularx' environment and 'X' column type
\usepackage{ragged2e}  % for '\RaggedRight' macro (allows hyphenation)
\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X} 
\usepackage{booktabs}  % for \toprule, \midrule, and \bottomrule macros\documentclass[10pt]{•}
%\parindent0pt  
%\parskip10pt             % make block paragraphs
%\raggedright                            % do not right justify

\title{Nek5000 User Documentation}    % Supply information
\author{Paul Fischer et al.}              %   for the title page.
\publicationdate{date set on next release}
\report_no{ANL/MCS-TM-351}
\date{\today}                           %   Use current date. 
%\makeindex
% Note that book class by default is formatted to be printed back-to-back.
\begin{document}                        % End of preamble, start of text
%\frontmatter                            % only in book class (roman page #s)
%\mainmatter      

\maketitle
\clearpage
\thispagestyle{empty}
\pagenumbering{roman}
\tableofcontents
\clearpage

\section*{Executive Summary} 


Abstract here.

\addcontentsline{toc}{section}{Executive Summary}
\newpage

\pagenumbering{arabic}
\setcounter{page}{1}
\counterwithout{section}{chapter}

\chapter{Introduction}

Nek5000 is designed to simulate laminar, transitional, and turbulent
incompressible or low Mach-number flows with heat transfer and species
transport. It is also suitable for incompressible magnetohydrodynamics
(MHD). Nek5000 is written in f77 and C. It uses MPI for message passing
(but can be compiled without MPI for serial applications)
and some LAPACK routines for eigenvalue computations (depending on
the particular solver employed).  In addition, it can be optionally
coupled with MOAB, which provides an interface to meshes generated with 
CUBIT. Nek5000 output formats can be read by either {\tt postx} or the parallel visualization 
package VisIt developed by Hank Childs and colleagues at LLNL/LBNL.
VisIt is mandatory for large problems (e.g., more than 100,000 
spectral elements).
\subsection*{Computational approach}
The spatial discretization is based on 
the spectral element method (SEM) \cite{pat84}, which is a high-order 
weighted residual technique similar to the finite element method.   
In the SEM, the solution and data are represented in terms of 
\(N\)th-order tensor-product polynomials within each of \(E\) deformable 
hexahedral (brick) elements. Typical discretizations involve \(E\)=100--10,000 elements of order 
\(N\)=8--16 (corresponding to 512--4096 points per element).
Vectorization and cache efficiency derive from the local lexicographical
ordering within each macro-element and from the fact that the action of
discrete operators, which nominally have \(O(EN^6)\) nonzeros, can be evaluated
in only \(O(EN^4)\) work and \(O(EN^3)\) storage through the use of 
tensor-product-sum factorization \cite{sao80}.   The SEM exhibits 
very little numerical dispersion and dissipation, which can be important, 
for example, in stability calculations, for long time integrations, 
and for high Reynolds number flows. We refer to \cite{dfm02} for more
details.
\input{philosophy}
\section{Nek5000 solvers}\label{sec:ns_eqns}
\input{ns_eqns}
%\section{Nek5000 code layout}
%\input{code_layout}

\chapter{Quick start}
\section{Download and Build}
\input{down_build}
\section{A worked example}
\input{example}

\chapter{User files}
\section{Case set-up .usr}
\input{user_intro}
\section{Problem size file SIZE}
\input{size_intro}
\section{Geometry and Parameters file .rea}

\input{rea_intro}
%\begin{comment}
\input{data_layout}
%\subsection{Additional files}

\chapter{Geometry}\label{sec:geom}
\input{geom_general}
Note that in case of any changes in the SIZE file, a recompilation is necessary.\\
\section{Setting up the geometry}
\subsection{Rectangular geometries}
\input{genbox}\label{sec:genbox}
%\input{mesh101}
%\section{Curvilinear geometry}
\section{Extrusion/Mirroring}
\input{n2to3}
\section{Boundary and initial conditions}
\input{boundaryc}
\input{internal_bc}
\input{intial_cond}
\section{Mesh Partioning for Parallel Computing}
\input{genmap}

\chapter{Performing large scale simulations  in Nek5000}
\section{Large scale simulations}
\input{large_scale}
\section{Parallelism in Nek5000}
\input{parallelism}
%\end{comment}
%\begin{comment}

\chapter{Mathematical routines of interest}
\input{help}

%\section{Troubleshooting}
%\input{troubleshoot}
\begin{comment}
\chapter{Postprocessing}
\section{Visualisation}
%\section{Toolboxes}

%\chapter{Algorithms}
%\section{Flow solvers}
%\section{Filtering}
\end{comment} 
\chapter{Appendix}
\section{Appendix A. Extensive list of parameters .rea file}
\input{rea_explicit}
\section{Appendix B. Extensive list of parameters SIZE file}
\input{size_explicit}
%\printindex 
%

\bibliographystyle{unsrt}
\renewcommand\refname{References}


\addtolength{\baselineskip}{-.1\baselineskip}
\bibliography{emmd}
\addtolength{\baselineskip}{+.111111\baselineskip}

\end{document}                          % The required last line
